|

### 2021-12-09 text/ManuscriptDraft.Rmd
Manuscript update (methods)
Updated manuscript

The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (realtime tracking frame per frame).

@@

@@

Mota counts shifts in tracking.

@@

>>>>

The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (real-time tracking frame per frame).

The speed of the tracking algorithm depends on the computational power available as well as the number of objects that are being tracked.

@@

The counter for number of disappeared frames is reset when a new point is associated with the track within the threshold.

@@

Mota counts tracking mismathces (shifts in a track).

@@

Lastly, we may be interested in the number of flowers that existed in a plot. Therefore, a final way of evaluating automatic flower tracking performance is to compare the number of tracks identified by the automatic tracking with the true number of flowers in a series. These should ideally be equal.
